Comparing R packages for calculation of persistent homology

### 2020-03-08 tdabench-paper/tdabench.Rmd
added narrative for fig fin to results

@@

@@

\begin{figure}
  \centering
  \includegraphics[height=2.5in]{../Figures/Final_Figures/fig6.png}
  \caption{TDAstats Rips complexes vs GUDHI Alpha complex average run times across all 3D shapes for 2D features. The x-axis represents the number of points in the point cloud, and y-axis represents average run time. The type of complex is indicated by color. Panel 1 = Execution time on annulus. Panel 2 = Execution time on sphere. Panel 3 = Execution time on torus. Panel 4 = Execution time on uniform box. Data is presented as mean +/- standard deviation}
\label{fig:fin}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=2.5in]{decision.png}
    \caption{Basic decision chart for choosing TDA library based on dataset.}
\label{decision}
\end{figure}

>>>>

In real life scenarios, practitioners likely care most about comparative performance of the fastest Vietoris-Rips complex library and the fastest alpha complex library.
Figure \ref{fig:fin} illustrates this comparison, showing that for 3-dimensional point clouds, GUDHI's alpha complex library outpaces Ripser's Vietoris-Rips functionality.

@@

\begin{figure}
  \centering
  \includegraphics[height=2.5in]{../Figures/Final_Figures/fig6.png}
  \caption{
    \textbf{Runtime comparison of persistent homology calculation between Ripser's Vietoris-Rips and GUDHI's alpha complex functionality.}
    Average runtime (mean $\pm$ SD, $n=10$ iterations per data point) for various 3-dimensional point cloud structures (facet) plotted against point cloud size for each library (color).
    Benchmarking was conducted on an annulus (top-left), a sphere (top-right), a torus (bottom-left), and a cube (bottom-right).
    Data was not collected for data dimensions greater than 3 due to computational limitations of calculating alpha complices.}
\label{fig:fin}
\end{figure}

@@

@@

<!--PUT AS TEXT INSTEAD
\begin{figure}
  \centering
  \includegraphics[height=2.5in]{decision.png}
    \caption{Basic decision chart for choosing TDA library based on dataset.}
\label{decision}
\end{figure}-->
